%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Bohan Zhang} \\ \vspace{1pt}
    \small (+86)18691876994 $|$ \href{mailto:sheldonzhang.bupt@gmail.com}{sheldonzhang.bupt@gmail.com} $|$ 
    \urlstyle{same}\href{https://github.com/tabVersion}{Github} $|$ \urlstyle{same}\href{https://linkedin.com/in/bohan-zhang-a3583b198}{Linkedin}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Beijing University of Posts and Telecommunications}{Beijing}
      {Bachelor of  Computer Science}{Sept. 2017 -- July 2021}
      \resumeItemListStart
        \resumeItem{Rewards: Second-class Scholarship (top 15\%); General GPA: 3.7; TOEFL: 94}
        \resumeItem{Major Relevant Courses Taken: Computer Networks, Machine Learning, Database System Principles, Operating Systems, Natural Language Processing.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SDE Intern}{Oct. 2020 -- Present}
      {ByteDance Inc.}{Beijing}
      \resumeItemListStart
        \resumeItem{Cooperated to work on a creative deriving platform. Used a decision tree to exclude unnecessary samples, increasing the app's overall revenue by 2\%.}
        \resumeItem{Used SQL and Flink to build a high-real-time posterior data collection system for pre-training models.}
        \resumeItem{Became proficient in the micro-service architecture of Protobuf-based RPC communication and Docker-based deployment.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Research Intern}{June 2020 -- Oct. 2020}
      {System Research Group, Microsoft Research Asia}{Beijing}
      \resumeItemListStart
        \resumeItem{Refined an Auto-ML framework, NNI, as team member on GitHub. Implemented NAS algorithms, eg. DARTS and ENAS.}
        \resumeItem{Used NAS to help the Bing team improve the text classification model; improved regression score by 5\% and decreased the model size by 3\%.}
        \resumeItem{Modified the Tensorflow source code to simulate an environment where a neural network runs on in a distributed way.}
        \resumeItem{Participated in Practicing Station and design labs for NAS beginners on campus.}
    \resumeItemListEnd

    \resumeSubheading
      {Research Assistant}{Apr. 2019 -- Aug. 2019}
      {Tsinghua University}{Beijing}
      \resumeItemListStart
        \resumeItem{Read papers related to knowledge graph embedding, eg. TransE, TransH and reproduce the experiments.}
        \resumeItem{Reproduced paper \emph{Is Word Segmentation Necessary for Deep Learning of Chinese Representations}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Campus Conference Voting System} $|$ \emph{Golang, Git, SQL}}{Nov. 2019 -- Apr. 2020}
          \resumeItemListStart
            \resumeItem{Developed an online voting system using Gin and put it to use online with maximum Query Per Second over 2000.}
            \resumeItem{Implemented an OAuth module to get user’s identity from Gateway on campus.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Distributed Lab} $|$ \emph{Golang, Git}}{June 2018 -- July 2018}
          \resumeItemListStart
            \resumeItem{Reproduced MapReduce and Raft using Golang.}
            \resumeItem{Implemented a URL counter for large-scale dataset. It can complete the processing of GB-level data in less than a minute.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{DNS Proxy} $|$ \emph{Golang, Git}}{Mar. 2019 -- Mar. 2019}
          \resumeItemListStart
            \resumeItem{Increased concurrency performance by opening threads to handle messages.}
            \resumeItem{Used Golang to implement the DNS protocol and completed a DNS relay with blocking, forwarding, and storing features.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


\section{Club and organization experience}
    \resumeSubHeadingListStart
        \resumeSubheading
          {\textbf{Technical Chair}}{Sept. 2018 -- June 2019}
          {Microsoft Student Club}{Beijing University of Posts and Telecommunications}
          \resumeItemListStart
            \resumeItem{Organized technical sharing within the school, with more than 100 participants.}
            \resumeItem{Participated in the 2018 Microsoft hackathon, and created a distributed sharing platform with teammates.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%-------------------------------------------

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Well-skilled programming in Python and Golang. \\
     Familiar frameworks: PyTorch, Tensorflow, Django and Gin}; Packages: numpy, sklearn, matplotlib
    }
 \end{itemize}

\end{document}
